P4Query: Static Analyser Framework for P4

### 2021-03-29 publications/The_tool_intro/paper.tex
tool_intro: minor changes

	While unit tests need to be fast, integration tests can be slower, so we can use P4 files as the inputs to test the analysers. When one analyser needs to be tested, it uses the P4 file, and executes every analyser, that it is based on and the tests will check the result of this running. The tests are predefined, therefore we use a file to store the information of the tested sources and analyser -- which file tests which analysers and with which test classes.

@@

  The approach of the checking is defined in our previous paper \cite{ownCheck}, but in short, it calculates the pre- and post-condition of the various blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program. Based on these condition pairs it can detect improper usage of the fields and headers. Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser and deparser is inconsistent with the need of the control function.

  In Figure \ref{code:cond}, there is an example condition for the MyIngress. We can see 4 pairs of conditions because it has 4 possible execution paths - there are three where the condition of the branch is true, and the table executes one of the possible actions i.e. $\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one where the condition of the branch is false.

@@

  In the current paper, we will not go into details on how the cost analysis tool calculates these metrics, but the principle is that we decompose the P4 program into primitive instructions whose expected cost is constant and already known. Implementations of P4 externals such as extern calls and lookup tables (e.g. \texttt{packet.extract} and \texttt{ipv4\_lpm} and in Figure~\ref{code:P4}) can also be passed to the tool in the form of these primitive instructions with known costs.

@@

	In the future, we would like to extend the tool with new analyses to give some other useful information for the developers about their P4 source. Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report, which are based on the connection between the statements.

>>>>

	While unit tests need to be fast, integration tests can be slower, so we can use P4 files as the inputs to test the analysers. When one analyser needs to be tested, it uses the P4 file, and executes every analyser, that it is based on and the tests will check the result of this running.

@@

  The approach of the checking is defined in our previous paper \cite{ownCheck}, but in short, it calculates the pre- and post-condition of the various blocks -- i.e the applied functions, the tables and the actions of the control --, the parser and the deparser of the program. Based on these condition pairs it can detect improper usage of the fields and headers. Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser and deparser is inconsistent with the need of the control function.

  In Figure \ref{code:cond}, there is an example condition for MyIngress control. We can see 4 pairs of conditions because it has 4 possible execution paths - there are three where the condition of the branch is true, and the table executes one of the possible actions i.e. $\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one where the condition of the branch is false.

@@

  In the current paper, we will not go into details on how the cost analysis tool calculates these metrics, but the principle is that we decompose the P4 program into primitive instructions whose expected cost is constant and already known. Implementations of P4 externals such as extern calls and lookup tables (e.g. \texttt{packet.extract} and \texttt{ipv4\_lpm} in Figure~\ref{code:P4}) can also be passed to the tool in the form of these primitive instructions with known costs.

@@

	In the future, we would like to extend the tool with new analyses to give some other useful information for the developers about their P4 source. Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report based on the connection between the statements.
